Preliminary categorisation of SpaceWarps candidates

### 2015-12-18 paper2.tex
comments on lenses

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Short title, max. 45 characters]{MNRAS \LaTeXe\ template -- title goes here}

@@

@@

>>>>

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Short title, max. 45 characters]{Preliminary categorisation of SpaceWarps candidates}

@@

\newcommand{\inclfig}[2]{
	\includegraphics[width=0.49\linewidth]{spaghetti/#2_input.png}
	\includegraphics[width=0.49\linewidth]{spaghetti/#2_img1.png}
	\includegraphics[width=0.49\linewidth]{spaghetti/#2_img3_ipol.png}
	\includegraphics[width=0.49\linewidth]{spaghetti/#2_img2.png}
	\includegraphics[width=1\linewidth]{masses/#1_#2_mstel_vs_mtot.png}
}

@@

\section{Introduction}

\section{Methods}

\section{Results}
We came up with four kind of candidates.

\subsection{HiRes image}
Almost certain candidates, that qualify for follow up hires observations

\subsection{Spectra}
Candidates to follow up with a spectral analysis.

\subsection{Bad models}
Candidates that need more work to be modelled.
Or that have features that are hard / impossible to model with the current SpaghettiLens version.
Examples are group lenses

\subsection{Non Lenses}
Those are most probly non lenses,

\subsection{plausible}
\begin{itemize}
  \item SW01 (ASW0004dv8) \\

  \item SW08 (ASW00099ed) \\
  Simple lens with two images;
  model has minor arthefacts

  \item SW11 (ASW0002qtn) \\
  Simple small arc;
  model nedes minor refinement;
  quite low mass ratio

  \item SW12 (ASW0003wsu) \\
  faint arc, bright overall situation, no counter image;
  has good model;
  low Mstel and low Mlens

  \item SW21 (ASW0004m3x) \\
  clear arc, no counter image; inbetween two external sources;
  model needs work, predicts additional images. play with external mass / sheer?
  Mass ratio low.

  \item SW27 (ASW0006jh5) \\
  (really plausible?)
  unclear situation, but arc is visible;
  model shows extended arc not there in org image;
  mass ratio ok

  \item SW31 (ASW00021r0) \\
  (really plausible?)
  noisy situation, unclear images, potential external mass interfering;
  model ok'ish, hard to say;
  high mass ratio

  \item SW33 (ASW0003s0m)\\
  clear picture, two image situation;
  model simple, but ok. arc too much extended;
  masses in the middle, but rather high ratio

  \item SW36 (ASW000096t) \\
  noisy picture, many possible external masses, faint images;
  model predicts additional images, needs more work, arc too extended;
  masses look ok

  \item SW38 (ASW0009cp0) \\
  quite clean picture, two bright minima, counter image hidden;
  model fine
  really hi stellar mass

  \item SW43 (ASW0001c3j) \\
  clean situation, faint arc'ish images;
  model needs work, shows additional images, strange arc (LHD);
  very high Mstel

  \item SW45 (ASW00024id)\\
  ring like structure, very clean \\
  usual problems with rings, otherwise model quite ok actually;
  very high Mstel

  \item SW46 (ASW00024q6) \\
  yellow'ish arc, two image configuration;
  model ok;
  masses ok

  \item SW52 (ASW0006a07) \\
  (no imgs)

  \item SW54 (ASW0007sez) \\
  white lens, fuzzy ring like structure;
  model really good, given ring like;
  masses ok

  \item SW58 (ASW0007iwp) \\
  nice arc, no counter image;
  model prediction really good;
  masses ok

\end{itemize}

good example of plausible

% \begin{figure}
% 	\inclfig{SW45}{ASW000024id_TSKKYHD3CB}
% \end{figure}

\begin{figure}
	\inclfig{SW58}{ASW0007iwp_4XBJWT3COV}
\end{figure}

\subsubsection{grouplens}

\begin{figure}
	\inclfig{SW36}{ASW000096t_7IPP7LWVOF}
\end{figure}

(like 4dv8 collective modelling)

\subsection{unclear}
\begin{itemize}
  \item SW04 (ASW0009cjs) \\
  noisy field, possible group lens, but images not typical? (no arclike structure);
  model fail (input errors);
  Mlens too high (10e13)

  \item SW06 (ASW0008swn)\\
  green images, elongated lens, images on strange positions?;
  model ok'ish, but mass distr. doesn't reflect visuals;
  masses ok

  \item SW07 (ASW0007e08) \\
  (no img)

  \item SW13 (ASW00047ae) \\
  croweded situation unclear setup;
  model failed, predicts additional images;
  masses ok

  \item SW15 (ASW0004nan) \\
  no counter image (should be visible)?
  model ok'ish;
  Mlens on the lower end

  \item SW17 (ASW0005rnb) \\
  two image setup, but arcish structure of images missing;
  model failed, predicts additional images, rednering failed;

  \item SW19 (ASW0001ld7) \\
  asymmetry / really extended arc and no counter image rather no lensing configuration;
  rendering ok'ish, model predicts additionla images;
  Mstel and Mlens way too low (e10 / e11)

  \item SW24 (ASW00050sk) \\
  unclear / noisy situation, shape of arc strange;
  model ok;
  mass ration close to unity

  \item SW32 (ASW0004iye) \\
  (no img)

  \item SW35 (ASW0004wgd) \\
  hard to say, doesn't look convincing, but neither totally off
  modell ok;
  masses as well;

  \item SW44 (ASW0002k40) \\
  (no img);
  very old model;
  hi mass ratio

  \item SW47 (ASW0003r6c) \\
  two images, no arcish structre.. too far away from lens?;
  model predicts additional images;
  quite high mass ratio

  \item SW51 (ASW0006e0o) \\
  (no img)

  \item SW56 (ASW0007pga) \\
  very ellyptical lens, images not really arcish;
  model failed, predicts additional images;
  masses ok

  \item SW57 (ASW0008pag) \\
  point mass / group lens interfering? symertry of arc off;
  model failed completly;
  Mlens too high

\end{itemize}

\begin{figure}
	\inclfig{SW19}{ASW0001ld7_OS3CYAKLRT}
\end{figure}

\begin{figure}
	\inclfig{SW57}{ASW0008pag_5SXGXQYY6V}
\end{figure}

\subsection{convincing}
\begin{itemize}
  \item SW02 (ASW000619d) \\

  \item SW05 (ASW0007k4r) \\

  \item SW09 (ASW0002asp) \\

  \item SW28 (ASW0007xrs) \\

  \item SW29 (ASW0008qsm) \\

\end{itemize}

\begin{figure}
	\inclfig{SW02}{ASW000619d_011489}
\end{figure}

\begin{figure}
	\inclfig{SW05}{ASW0007k4r_AJIBCHQ6EM}
\end{figure}

\begin{figure}
	\inclfig{SW09}{ASW0002asp_5EKMWWVJHL}
\end{figure}

\begin{figure}
	\inclfig{SW28}{ASW0007xrs_JHC3J2HYV7}
\end{figure}

\begin{figure}
	\inclfig{SW29}{ASW0008qsm_TOFS7JNGEK}
\end{figure}

\subsection{doubtful}
\begin{itemize}
  \item SW10 (ASW0002bmc) \\
  very elliptical setup, unlikley to be a lens;
  model failed totally

  \item SW16 (ASW0009bp2) \\
  very faint images

  \item SW18 (ASW0007hu2) \\
  model failed completly

  \item SW20 (ASW0002dx7) \\
  faint white images, rather substuctre of ``lens'' ??

  \item SW22 (ASW0009ab8) \\
  very faint images, group configuration;
  model predicts additional images;
  mass ration close to unity

  \item SW23 (ASW0003r61) \\
  (no img)

  \item SW26 (ASW0005ma2) \\
  similar to SW10

  \item SW34 (ASW00051ld) \\
  (no img)

  \item SW41 (ASW0008xbu) \\
  similar to SW10. very ellyptical lens

  \item SW42 (ASW00096rm) \\
  ring like structure, but very strange distribution;
  model not too bad, brightnesses off;
  stellar mass way too lower

  \item SW53 (ASW00070vl) \\
  images don't look liked lensed;
  model predicts additional images

\end{itemize}

outlier because very odd mass ratio
\begin{figure}
	\inclfig{SW42}{ASW00096rm_4Q3YCEWGLN}
\end{figure}

\subsection{missing}
\begin{itemize}
  \item SW03 (ASW0006mea)
  \item SW14 (ASW0004xjk)
  \item SW25 (ASW00007mq)
  \item SW30 (ASW0002p8y)
  \item SW37 (ASW00086xq)
  \item SW39 (ASW0005qiz)
  \item SW40 (ASW0008wmr)
  \item SW48 (ASW0000g95)
  \item SW49 (ASW00007ls)
  \item SW50 (ASW00008a0)
  \item SW55 (ASW0007t5y)
  \item SW59 (ASW00085cp)
\end{itemize}
